An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-11 paper.tex
Added note about stride width increasing with long perturbations. Fixes #129.
Added note on the x moment error with variable belt speed.

When belt speed is not constant, the inertia of the rollers and motor will
induce error in the force plate $x$ axis moment, and hence, the
anterior-posterior coordinate ($z$ axis) of the center of pressure that is
measured by the instrumentation in the treadmill. If needed, this error can be
compensated by a linear model as shown in \cite{Hnat2014}. The model
coefficients can be identified from the unloaded trials given in
Table~\ref{tab:comptrials}. The error due to inertia is random and does not
affect the averaged joint moments presented in
Figure~\ref{fig:angle-torque-comparison}. Compensation should, however, be done
if joint moments from individual gait cycles are of interest rather than the
ensemble average.
%
\begin{table}
  \cprotect\caption{A list of unloaded trials collected for each speed. Each
    loaded trial includes a compensation file listed in its meta data which
    matches it to these unloaded trials. Generated by
    \verb|src/subject_table.py|.}
  \centering
  \small
  \input{tables/compensation_trials.tex}
  \label{tab:comptrials}
\end{table}

>>>>

When belt speed is not constant, the inertia of the rollers and motor will
likely induce error in the force plate $x$ axis moment, and hence, the
anterior-posterior coordinate ($z$ axis) of the center of pressure that is
measured by the instrumentation in the treadmill. This error may or may not be
pertinent to different analyses. If needed, this error can be partially
compensated by a linear model as shown in \cite{Hnat2014}. The model
coefficients can be identified from the unloaded trials given in
Table~\ref{tab:comptrials}. The error due to inertia is random and does not
affect the averaged joint moments presented in
Figure~\ref{fig:angle-torque-comparison}. Compensation should, however, be done
if joint moments from individual gait cycles are of interest rather than the
ensemble average.
%
\begin{table}
  \cprotect\caption{A list of unloaded trials collected for each speed. Each
    loaded trial includes a compensation file listed in its meta data which
    matches it to these unloaded trials. Generated by
    \verb|src/subject_table.py|.}
  \centering
  \small
  \input{tables/compensation_trials.tex}
  \label{tab:comptrials}
\end{table}
